\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-06 demystify.tex
updates

\section{Getting Admitted and Choosing the Right School}

@@

Choosing a school and an advisor is clearly one of the most important things in your mind when you apply to and especially when you get admitted to a PhD program in CS.  This is further complicated due to cultural differences and unfamiliarity of  international students to the US system and faculty.  I hope this section will clear some confusions and help you make more informed decision.

@@

There are many types of universities in the US (as well as other countries). But here I mainly focus on the object of obtaining a Ph.D degree in CS.

\subsection{Schools that offer Ph.D. in CS}  Most university will have a "Computer Science" or CS-like programs. 
However, while many universities offer Ph.D. degree in their CS programs, many do not.  These universities might offer just Bachelor degrees (e.g., BS) and no graduate studies (i.e., no MS or Ph.D degrees), or they must just offer MS programs (but no PhD).

>>>>

\section{Getting Admitted}

@@

Choosing a school and an advisor is clearly one of the most important things in your mind when you apply to and especially when you get admitted multiple programs.  This is further complicated due to cultural differences and unfamiliarity of  international students to the US system and faculty.  This section aims to mitigate some confusions and help you make more informed decision.

@@

There are many types of universities in the US (as well as other countries). But here I focus the discussion in the context of obtaining a Ph.D degree in CS.

\subsection{Schools that offer Ph.D. in CS}  Most university will have CS programs. 
However, while many universities offer Ph.D. degree in their CS programs, many do not.  These universities might offer just Bachelor degrees (e.g., BS) and no graduate studies (i.e., no MS or Ph.D degrees), or they must just offer MS programs (but no PhD).
